---
title: "<span style='font-size: 48px'>Developing Data Products - Week 2 Assignment</span>"
author: "<span style='font-size: 24px'>Henry CY Wong</span>"
date: "<span style='font-size: 24px'>2021-04-21</span>"
output: 
    html_document:
            css: style.css
            keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

&nbsp;
&nbsp;

## 1. Introduction

The objective of this assignment is used to create a map with using **Leaflet** in a web page. I would like to use this opportunity to show the location of some sightseeing points in Hong Kong as well.

&nbsp;
&nbsp;

## 2. Build the Map with Leaflet

First of all, let's load the **Leaflet** library.

```{r load_library}
library(leaflet)
```


Then, the latitudes, longitude sand pop-up texts of Hong Kong sightseeig points are assigned as follows:

```{r assign_values}
mylat <- c(22.312771, 22.246560992402, 22.271121, 22.254106)
mylng <- c(114.041931, 114.1753523356, 114.150233, 113.905144)
mypopup <- c("Disneyland, Hong Kong", "Ocean Park, Hong Kong", "The Peak, Hong Kong", "Tian Tan Buddha, Hong Kong")
mypopularity <- c(1, 4, 10, 7)
```

Finally, the map of Hong Kong sightseeing points are built as below:

```{r build_map}
mymap <- leaflet() %>%
    addTiles() %>%
    addMarkers(lat = mylat, lng = mylng, popup = mypopup, clusterOptions = markerClusterOptions()) %>%
    addCircleMarkers(lat = mylat, lng = mylng, radius = (sum(mypopularity) - mypopularity) * 2)
mymap
```

&nbsp;
&nbsp;
